Reflections from reproductions

### 2024-10-25 framework/stars_checklist.tex
chore(docs): correct licence spelling

\begin{longtable}[]{@{}ll@{}}
\toprule
Item & Implementation\tabularnewline
\midrule
\endhead
\textbf{Essential components} &\tabularnewline
Open license & \emph{Describe your implementation of this
component}\tabularnewline
Dependency management &\tabularnewline
FOSS model &\tabularnewline
Minimum documentation &\tabularnewline
ORCID &\tabularnewline
Citation information &\tabularnewline
Remote code repository &\tabularnewline
Open science archive &\tabularnewline
\textbf{Optional components} &\tabularnewline
Enhanced documentation &\tabularnewline
Documentation hosting &\tabularnewline
Online coding environment &\tabularnewline
Model interface &\tabularnewline
Web app hosting &\tabularnewline
\bottomrule
\end{longtable}

@@

\paragraph{Open license}

Free and open-source software (FOSS) license (e.g. MIT, GNU Public
License (GPL))

@@

\begin{itemize}
\tightlist
\item
  Plain english summary of project and model
\item
  Clarifying license
\item
  Citation instructions
\item
  Contribution instructions
\item
  Model installation instructions
\item
  Structured code walk through of model
\item
  Documentation of modelling cycle using TRACE
\item
  Annotated simulation reporting guidelines
\item
  Clear description of model validation including its intended purpose
\end{itemize}

>>>>

\begin{longtable}[]{@{}ll@{}}
\toprule
Item & Implementation\tabularnewline
\midrule
\endhead
\textbf{Essential components} &\tabularnewline
Open licence & \emph{Describe your implementation of this
component}\tabularnewline
Dependency management &\tabularnewline
FOSS model &\tabularnewline
Minimum documentation &\tabularnewline
ORCID &\tabularnewline
Citation information &\tabularnewline
Remote code repository &\tabularnewline
Open science archive &\tabularnewline
\textbf{Optional components} &\tabularnewline
Enhanced documentation &\tabularnewline
Documentation hosting &\tabularnewline
Online coding environment &\tabularnewline
Model interface &\tabularnewline
Web app hosting &\tabularnewline
\bottomrule
\end{longtable}

@@

\paragraph{Open licence}

Free and open-source software (FOSS) licence (e.g. MIT, GNU Public
Licence (GPL))

@@

\begin{itemize}
\tightlist
\item
  Plain english summary of project and model
\item
  Clarifying licence
\item
  Citation instructions
\item
  Contribution instructions
\item
  Model installation instructions
\item
  Structured code walk through of model
\item
  Documentation of modelling cycle using TRACE
\item
  Annotated simulation reporting guidelines
\item
  Clear description of model validation including its intended purpose
\end{itemize}

### 2024-10-25 index.qmd
chore(docs): correct licence spelling

## License {.unnumbered}

This book is licensed under a [Creative Commons Attribution 4.0 International (CC BY 4.0)](https://github.com/pythonhealthdatascience/stars_wp1_summary/blob/1a7e932013abd8e4810764b8925e98e9a6473844/LICENSE) license.

[![License: CC BY 4.0](https://licensebuttons.net/l/by/4.0/80x15.png)](https://creativecommons.org/licenses/by/4.0/)
[![License: CC BY 4.0](https://img.shields.io/badge/License-CC_BY_4.0-lightgrey.svg)](https://creativecommons.org/licenses/by/4.0/)

>>>>

## Licence {.unnumbered}

This book is licensed under a [Creative Commons Attribution 4.0 International (CC BY 4.0)](https://github.com/pythonhealthdatascience/stars_wp1_summary/blob/1a7e932013abd8e4810764b8925e98e9a6473844/LICENSE) licence.

[![Licence: CC BY 4.0](https://licensebuttons.net/l/by/4.0/80x15.png)](https://creativecommons.org/licenses/by/4.0/)
[![Licence: CC BY 4.0](https://img.shields.io/badge/License-CC_BY_4.0-lightgrey.svg)](https://creativecommons.org/licenses/by/4.0/)

### 2024-10-25 pages/framework.qmd
chore(docs): add TODO to several pages
chore(docs): correct licence spelling

@@

* Open license - available on about half, added on request for rest, a very important one as without it you technically cannot reuse someones code
* Complete materials - rarely, so alot of time spent on writing code and figuring out how best to do that
* Dependency management - rarely done, and although not an issue in simpler cases, a big impact in more complex
* Model interface - provided for two although not helpful as (1) host no longer operating, and as not focus, didn't try to run locally, and (2) other app was viewable but didn't produce the figures and outcomes from paper (was more general, whilst paper delved into scenarios beyond app)

>>>>

<!--TODO: Move this to stars_wp2-->

@@

* Open licence - available on about half, added on request for rest, a very important one as without it you technically cannot reuse someones code
* Complete materials - rarely, so alot of time spent on writing code and figuring out how best to do that
* Dependency management - rarely done, and although not an issue in simpler cases, a big impact in more complex
* Model interface - provided for two although not helpful as (1) host no longer operating, and as not focus, didn't try to run locally, and (2) other app was viewable but didn't produce the figures and outcomes from paper (was more general, whilst paper delved into scenarios beyond app)

### 2024-10-25 pages/protocol.qmd
chore(docs): correct licence spelling

For this work, six published healthcare DES models were selected. These were models with publicly available code under an open license (either already available or add on request from the STARS team). For each model, the follow stages of work were conducted:

@@

* Informed authors about study and, if not available, asked if they would be happy to add an open license to their code
* Set up repository for reproduction with the article and code
* Read the article and defined the scope of the reproduction, archiving the scope (and repository) on Zenodo before proceeding
* Looked over the model code, created a suitable environment with the software and packages required, and then ran the model. For each study, with any issues faced in running the model, troubleshooting was performed such as modifying or writing code. If troubleshooting was exhaused and there were still issues or discrepancies in the results, the original study authors were informed and provided the opportunity to advice on the reason for this (although with no pressure or requirement to do so)
* For each item in the scope, a decision was made as to whether this had been successfully reproduced or not. This was a subjective decision which allowed some expected deviation due to model stochasticity (for example, lack of seed control).
* This is timed (including time to produce each item in the scope), and limited to a maximum of 40 horus

>>>>

For this work, six published healthcare DES models were selected. These were models with publicly available code under an open licence (either already available or add on request from the STARS team). For each model, the follow stages of work were conducted:

@@

* Informed authors about study and, if not available, asked if they would be happy to add an open licence to their code
* Set up repository for reproduction with the article and code
* Read the article and defined the scope of the reproduction, archiving the scope (and repository) on Zenodo before proceeding
* Looked over the model code, created a suitable environment with the software and packages required, and then ran the model. For each study, with any issues faced in running the model, troubleshooting was performed such as modifying or writing code. If troubleshooting was exhaused and there were still issues or discrepancies in the results, the original study authors were informed and provided the opportunity to advice on the reason for this (although with no pressure or requirement to do so)
* For each item in the scope, a decision was made as to whether this had been successfully reproduced or not. This was a subjective decision which allowed some expected deviation due to model stochasticity (for example, lack of seed control).
* This is timed (including time to produce each item in the scope), and limited to a maximum of 40 horus

### 2024-10-25 pages/reflections.qmd
docs(reflections): add tom's suggestion re: solutions for large file sizes
chore(docs): correct licence spelling

* The `import` statements can be sufficient in indicating all the packages required but this is not always the case if there are "hidden"/unmentioned dependencies that don't get imported
* There are various options for listing the packages (e.g. comprehensive import statements, installation lines in the script, environment files).
* Ideally mention this in repository, not just the paper.
* If there are local dependencies (e.g. other GitHub repositories), make sure to (a) mention and link to these repositories, so it is clear they are also required, and (b) include license/s in those repositories also, so they can be used.
* This was a common issue.

@@

* For most studies, this was not relevant, with outputs relatively small
* I only really found this to be an issue when files exceeded GitHub threshold. [GitHub](https://docs.github.com/en/repositories/working-with-files/managing-large-files/about-large-files-on-github) give warning over 50 MB, blocks files over 100 MB, requiring you to use GitHub LFS. Recommends repositories ideally <1 GB and for sure < 5GB. [GitHub LFS](https://docs.github.com/en/repositories/working-with-files/managing-large-files/about-storage-and-bandwidth-usage) has limits on storage and bandwith use (1GB of each).

>>>>

* The `import` statements can be sufficient in indicating all the packages required but this is not always the case if there are "hidden"/unmentioned dependencies that don't get imported
* There are various options for listing the packages (e.g. comprehensive import statements, installation lines in the script, environment files).
* Ideally mention this in repository, not just the paper.
* If there are local dependencies (e.g. other GitHub repositories), make sure to (a) mention and link to these repositories, so it is clear they are also required, and (b) include licence/s in those repositories also, so they can be used.
* This was a common issue.

@@

* For most studies, this was not relevant, with outputs relatively small
* I only really found this to be an issue when files exceeded GitHub threshold. [GitHub](https://docs.github.com/en/repositories/working-with-files/managing-large-files/about-large-files-on-github) give warning over 50 MB, blocks files over 100 MB, requiring you to use GitHub LFS. Recommends repositories ideally <1 GB and for sure < 5GB. [GitHub LFS](https://docs.github.com/en/repositories/working-with-files/managing-large-files/about-storage-and-bandwidth-usage) has limits on storage and bandwith use (1GB of each).
* **Reducing file size isn't the only solution**. In cases where you have large files, a good option can be storing it elsewhere and then pulling from there into your workflow - for example, storing in **zenodo** and fetching using [pooch](https://github.com/fatiando/pooch).
